Exp1 - Opt w_max and {A,phi)

### 2018-03-23 voltagebudget/analysis/paper_figures.Rmd
Update fig7 vis

# --------------------------
exp <- "77"
freqs <- c(24, 30)

@@

# --------------------------
exp <- "79"
freqs <- c(6, 8, 10, 12, 14, 16, 18, 20)

@@

@@

rm(df, exp, freq, freqs, name)
```

@@

fig1 %>% 
  filter(V_osc/V_comp <= 3) %>% 
  filter(freq==20) %>% 
  filter(V_osc/V_comp <= 3) %>% 
  filter(N %in% sample(1:max_N, 18, replace = FALSE)) %>% 
  ggplot(aes(x=V_osc/V_comp, y=errors*1e3)) +
  geom_point(size=.1, alpha=0.1, color="grey") + 
  geom_vline(xintercept = 1, alpha=0.7, color="purple", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.5, color="purple", linetype="dashed") +
  facet_wrap(~rank, nrow=3) +
  theme_classic() + 
  scale_x_continuous(breaks=c(0, 1, 2)) +
  scale_y_continuous(breaks=c(0, 10)) +
  theme(
    strip.text.x = element_text(size=0),
    strip.background = element_blank(),
    # axis.line=element_blank(),
    # axis.text.x=element_blank(),
    # axis.text.y=element_blank(),
    # axis.ticks=element_blank(),s
    # axis.title.x=element_blank(),
    # axis.title.y=element_blank(),
    panel.background=element_blank(),
    # panel.border=element_blank(),
    # panel.grid.major=element_blank(),
    # panel.grid.minor=element_blank(),
    plot.background=element_blank()) +
  labs(x=expression(V[o]/V[c]), y="Error (ms)") -> p3

fig1 %>% 
  filter(freq==20) %>% 
  filter(V_osc/V_comp <= 3) %>% 
  ggplot(aes(y=V_osc/V_comp, x=delta_spikes)) +
  geom_jitter(size=0.1, alpha=0.01) + 
  geom_hline(yintercept = 1, alpha=0.7, color="purple", linetype="dashed") +
  geom_hline(yintercept = 0.5, alpha=0.5, color="purple", linetype="dashed") +
  theme_classic() +
  labs(y=expression(V[o]/V[c]), x="Spike count") -> p4

plot_grid <- rbind(
  c(1, 1, 1, 2, 2), 
  c(1, 1, 1, 2, 2), 
  c(1, 1, 1, 2, 2),
  c(1, 1, 1, NA, NA),
  c(3, 3, 3, 4, 4),
  c(3, 3, 3, 4, 4),
  c(3, 3, 3, 4, 4))
grid.arrange(p1, p2, p3, p4, layout_matrix=plot_grid)
rm(p1, p2, p3, p4, plot_grid, max_N)
```

@@

plot_grid <- rbind(
  c(1,  1,  1,  1,  2,  2,  2, 2, 3, 3,   3, 3),
  c(1,  1,  1,  1,  2,  2,  2, 2, 3, 3,   3, 3),
  c(1,  1,  1,  1,  2,  2,  2, 2, 3, 3,   3, 3),
  c(4,  4,  4,  4,  2,  2,  2, 2, 3, 3,   3, 3),
  c(4,  4,  4,  4,  2,  2,  2, 2, 3, 3,   3, 3),
  c(4,  4,  4,  4,  2,  2,  2, 2, 3, 3,   3, 3),
  c(NA, NA, NA, NA, NA, NA, 5, 5, 5, 5,  NA, NA),
  c(NA, NA, NA, NA, NA, NA, 5, 5, 5, 5,  NA, NA),
  c(NA, NA, NA, NA, NA, NA, 5, 5, 5, 5,  NA, NA))

grid.arrange(p1, p2, p3, p4, p5, layout_matrix=plot_grid)
rm(p1, p2, p3, p4, plot_grid, max_N, M)
```

@@

```{r, fig.width=1.8, fig.height=1.5}
fig2 %>% 
  filter(V_osc/V_comp <= 3) %>% 
  ggplot(aes(x=V_osc/V_comp, y=delta_spikes, color=freq, group=freq)) +
  geom_jitter(alpha=0.2, size=0.1) + 
  labs(x=expression(V[o]/V[c]), y="Spike count") +
  scale_color_gradient(low="gold", high="darkgreen") +
  # scale_x_continuous(breaks=c(0, 4.0, 8.0, 12.0)) +
  theme_classic() +
  theme(legend.position="right", 
    legend.key.size = unit(.3, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8)) -> p1

fig2 %>% 
  filter(V_osc/V_comp <= 3) %>% 
  ggplot(aes(x=V_osc/V_comp, y=errors*1e3, color=freq, group=freq)) +
  geom_jitter(alpha=0.2, size=0.1) + 
  labs(x=expression(V[o]/V[c]), y="Error (ms)") +
  scale_color_gradient(low="gold", high="darkgreen") +
  theme_classic() +
  # scale_x_continuous(breaks=c(0, 4.0, 8.0, 12.0)) +
  theme(legend.position="none", 
    legend.key.size = unit(.5, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8)) -> p3

fig2 %>% 
  filter(V_osc/V_comp <= 3) %>% 
  ggplot(aes(x=V_osc/V_comp, y=variances*1e3, color=freq, group=freq)) +
  geom_jitter(alpha=0.2, size=0.1) + 
  labs(x=expression(V[o]/V[c]), y="Variance (ms)") +
  scale_color_gradient(low="gold", high="darkgreen") +
  # scale_x_continuous(breaks=c(0, 4.0, 8.0, 12.0)) +
  theme_classic() +
  theme(legend.position="none", 
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8)) -> p2

plot_grid <- rbind(
  c(1, 1, 1, 1, NA, NA),
  c(1, 1, 1, 1, NA, NA),
  c(1, 1, 1, 1, NA, NA),
  c(2, 2, 2, 3, 3, 3),
  c(2, 2, 2, 3, 3, 3),
  c(2, 2, 2, 3, 3, 3))

>>>>

# --------------------------
# INITIAL
exp <- "77"
freqs <- c(20, 30)

@@

# --------------------------
# SLOW
exp <- "79"
freqs <- c(6, 8, 10, 12, 14, 16, 18)

@@

# --------------------------
# FAST
exp <- "80"
freqs <- c(22, 24, 26, 28)#, 32, 34 ,36, 38)
for(freq in freqs){
  name <- paste("../data/exp", exp, "_d-2e-3_f", as.character(freq), ".csv", sep="")
  df <- read_csv(paste(name, sep=","))
  df %>%
    filter(n_spikes > 0) -> df

@@

# --------------------------------------------------------------------
# Data
algs <- c("max", "left", "uni", "cc")
alg_names <- c("max", "left", "uniform", "coincidence")
exps <- c(82, 83, 84, 85)

fig3 <- NULL
for (n in 1:4){
  df <- read_csv(paste("../data/exp", as.character(exps[n]), "_", algs[n], ".csv", sep=""))
  df$alg <- rep(alg_names[n], nrow(df))

  fig3 <- rbind(fig3, df)
}

# Spikes
# Load ref spikes
ref <- read_csv("../data/stim1.csv")
ref$set <- rep("initial", nrow(ref))

# Load exp spikes
exps <- c(86, 87, 88, 89)
fig4 <- NULL
for (n in 1:4){
  df <- read_csv(paste("../data/exp", as.character(exps[n]), "_", algs[n], "_c0.1_spikes.csv", sep=""))
  df$set <- rep("synchronized", nrow(df))

  # Add ref
  df <- rbind(df, ref)

  df$alg <- rep(alg_names[n], nrow(df))
  fig4 <- rbind(fig4, df)
}

rm(df, exp, freq, freqs, name, ref, n)
```

@@

fig1 %>% 
  filter(V_osc/V_comp <= 3) %>% 
  filter(freq==20) %>% 
  filter(V_osc/V_comp <= 3) %>% 
  filter(N %in% sample(1:max_N, 24, replace = FALSE)) %>% 
  ggplot(aes(x=V_osc/V_comp, y=errors*1e3)) +
  geom_point(size=.1, alpha=0.1, color="grey") + 
  geom_vline(xintercept = 1, alpha=0.7, color="purple", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.5, color="purple", linetype="dashed") +
  facet_wrap(~rank, nrow=3) +
  theme_classic() + 
  scale_x_continuous(breaks=c(0, 1, 2)) +
  scale_y_continuous(breaks=c(0, 10)) +
  theme(
    strip.text.x = element_text(size=0),
    strip.background = element_blank(),
    # axis.line=element_blank(),
    # axis.text.x=element_blank(),
    # axis.text.y=element_blank(),
    # axis.ticks=element_blank(),s
    # axis.title.x=element_blank(),
    # axis.title.y=element_blank(),
    panel.background=element_blank(),
    # panel.border=element_blank(),
    # panel.grid.major=element_blank(),
    # panel.grid.minor=element_blank(),
    plot.background=element_blank()) +
  labs(x=expression(V[o]/V[c]), y="Error (ms)") -> p3

plot_grid <- rbind(
  c(1, 1, 1, 2, 2), 
  c(1, 1, 1, 2, 2), 
  c(1, 1, 1, 2, 2),
  c(1, 1, 1, NA, NA),
  c(3, 3, 3, 3, 3),
  c(3, 3, 3, 3, 3),
  c(3, 3, 3, 3, 3))
  # c(3, 3, 3, 4, 4),
  # c(3, 3, 3, 4, 4),
  # c(3, 3, 3, 4, 4))
grid.arrange(p1, p2, p3, layout_matrix=plot_grid)
rm(p1, p2, p3, plot_grid, max_N)
```

@@

fig1 %>% 
  filter(freq==20) %>% 
  filter(V_osc/V_comp <= 3) %>% 
  ggplot(aes(y=V_osc/V_comp, x=delta_spikes)) +
  geom_jitter(size=0.1, alpha=0.01) + 
  geom_hline(yintercept = 1, alpha=0.7, color="purple", linetype="dashed") +
  geom_hline(yintercept = 0.5, alpha=0.5, color="purple", linetype="dashed") +
  theme_classic() +
  labs(y=expression(V[o]/V[c]), x="Spike count") -> p6

plot_grid <- rbind(
  c(1,  1,  1,  1,  2,  2,  2, 2, 3, 3,  3, 3),
  c(1,  1,  1,  1,  2,  2,  2, 2, 3, 3,  3, 3),
  c(1,  1,  1,  1,  2,  2,  2, 2, 3, 3,  3, 3),
  c(4,  4,  4,  4,  2,  2,  2, 2, 3, 3,  3, 3),
  c(4,  4,  4,  4,  2,  2,  2, 2, 3, 3,  3, 3),
  c(4,  4,  4,  4,  2,  2,  2, 2, 3, 3,  3, 3),
  c(NA, NA, NA, NA, NA, NA, 5, 5, 5, 6,  6, 6),
  c(NA, NA, NA, NA, NA, NA, 5, 5, 5, 6,  6, 6),
  c(NA, NA, NA, NA, NA, NA, 5, 5, 5, 6,  6, 6))

grid.arrange(p1, p2, p3, p4, p5, p6, layout_matrix=plot_grid)
rm(p1, p2, p3, p4, plot_grid, max_N, M)
```

@@

```{r, fig.width=1.8, fig.height=2.25}
# ------------------------------------------
# SLOW
fig2 %>% 
  filter(freq <= 20) %>%
  filter(V_osc/V_comp <= 3) %>% 
  ggplot(aes(x=V_osc/V_comp, y=errors*1e3, color=freq, group=freq)) +
  geom_jitter(alpha=0.2, size=0.1) + 
  labs(x=expression(V[o]/V[c]), y="Avg. error (ms)") +
  scale_color_gradient2(
    low="gold", high="darkgreen", mid="darkgrey", 
    midpoint=20, name="Freq (Hz)", breaks = c(5, 10, 15, 20), limits=c(5, 20)) +
  theme_classic() +
  geom_vline(xintercept = 1, alpha=0.5, color="black", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.3, color="black", linetype="dashed") +
  scale_y_continuous(breaks=c(0, 4.0, 8.0, 12.0), limits=c(0, 12)) +
  theme(legend.position="top", 
    legend.key.size = unit(.3, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8)) -> p1

fig2 %>% 
  filter(freq <= 20) %>%
  filter(V_osc/V_comp <= 3) %>% 
  ggplot(aes(x=V_osc/V_comp, y=variances*1e3, color=freq, group=freq)) +
  geom_jitter(alpha=0.2, size=0.1) + 
  labs(x=expression(V[o]/V[c]), y="Pop. variance (ms)") +
  scale_color_gradient2(low="gold", high="darkgreen", mid="darkgrey", midpoint=20) +
  scale_y_continuous(breaks=c(8.0, 10, 12.0), limits=c(8, 12)) +
  theme_classic() +
  theme(legend.position="none", 
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8)) -> p2

fig2 %>% 
  filter(freq <= 20) %>%
  filter(V_osc/V_comp <= 3) %>% 
  ggplot(aes(x=V_osc/V_comp, y=variances*1e3, color=freq, group=freq)) +
  geom_jitter(alpha=0.2, size=0.1) + 
  # labs(x=expression(V[o]/V[c]), y="Variance (ms)") +
  scale_color_gradient2(low="gold", high="darkgreen", mid="darkgrey", midpoint=20) +
  lims(y=c(9,11)) +
  theme_classic() +
  theme(axis.line=element_blank(),
      axis.text.x=element_blank(),
      # axis.text.y=element_blank(),
      axis.ticks.x=element_blank(),
      axis.title.x=element_blank(),
      axis.title.y=element_blank(),
      legend.position="none",
      panel.background=element_blank(),
      panel.border=element_blank(),
      panel.grid.major=element_blank(),
      panel.grid.minor=element_blank(),
      plot.background=element_blank()) -> p2.sub

fig2 %>% 
  filter(freq <= 20) %>%
  filter(V_osc/V_comp <= 3) %>% 
  ggplot(aes(x=V_osc/V_comp, y=delta_spikes, color=freq, group=freq)) +
  geom_jitter(alpha=0.2, size=0.1) + 
  labs(x=expression(V[o]/V[c]), y="Spike count") +
  scale_color_gradient2(low="gold", high="darkgreen", mid="darkgrey", midpoint=20) +
  scale_y_continuous(breaks=c(0, 1, 2, 3), limits=c(0, 3)) +
  theme_classic() +
  theme(legend.position="none", 
    legend.key.size = unit(.3, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8)) -> p3

# ------------------------------------------
# FAST
fig2 %>% 
  filter(freq >= 20) %>%
  filter(V_osc/V_comp <= 3) %>% 
  ggplot(aes(x=V_osc/V_comp, y=errors*1e3, color=freq, group=freq)) +
  geom_jitter(alpha=0.2, size=0.1) + 
  labs(x=expression(V[o]/V[c]), y="Avg. error (ms)") +
  scale_color_gradient2(
    low="gold", high="darkgreen", mid="darkgrey", 
    midpoint=20, name="", breaks = c(20, 25, 30)) +
  theme_classic() +
  geom_vline(xintercept = 1, alpha=0.5, color="black", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.3, color="black", linetype="dashed") +
  scale_y_continuous(breaks=c(0, 4.0, 8.0, 12.0), limits=c(0, 12)) +
  theme(legend.position="top", 
    legend.key.size = unit(.3, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8)) -> p4

fig2 %>% 
  filter(freq >= 20) %>%
  filter(V_osc/V_comp <= 3) %>% 
  ggplot(aes(x=V_osc/V_comp, y=variances*1e3, color=freq, group=freq)) +
  geom_jitter(alpha=0.2, size=0.1) + 
  labs(x=expression(V[o]/V[c]), y="Pop. variance (ms)") +
  scale_color_gradient2(low="gold", high="darkgreen", mid="darkgrey", midpoint=20) +
  scale_y_continuous(breaks=c(8.0, 10, 12.0), limits=c(8, 12)) +
  theme_classic() +
  theme(legend.position="none", 
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8)) -> p5

fig2 %>%
  filter(freq >= 20) %>%
  filter(V_osc/V_comp <= 3) %>%
  ggplot(aes(x=V_osc/V_comp, y=delta_spikes, color=freq, group=freq)) +
  geom_jitter(alpha=0.2, size=0.1) +
  labs(x=expression(V[o]/V[c]), y="Spike count") +
  scale_color_gradient2(low="gold", high="darkgreen", mid="darkgrey", midpoint=20) +
  scale_y_continuous(breaks=c(0, 1, 2, 3), limits=c(0, 3)) +
  theme_classic() +
  theme(legend.position="none",
    legend.key.size = unit(.3, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8)) -> p6

plot_grid <- rbind(
  c(1, 4),
  c(1, 4),
  c(1, 4),
  c(2, 5),
  c(2, 5),
  c(3, 6),
  c(3, 6))
grid.arrange(p1, p2, p3, p4, p5, p6, layout_matrix=plot_grid)
rm(p1, p2, p3, p4, p5, p6, plot_grid)
```

# Optimal

```{r, fig.width=3, fig.height=1.4}
fig4 %>% 
  filter(alg != "coincidence") %>%
  ggplot(aes(x=(ts - min(ts))*1e3, y=ns, color=set)) +
  geom_point(size=0.5, alpha=0.7) +
  facet_grid(alg~.) +
  scale_color_manual(values=c("black", "darkgrey"), name="") +
  theme_classic() +
  labs(x="Time (ms)", y="Neuron") +
  theme(
    legend.position="top", 
    legend.key.size = unit(.5, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    strip.background = element_blank(),
    strip.text.y = element_text(angle = 0)) -> p1

fig3 %>% 
  filter(alg != "coincidence") %>%
  ggplot(aes(x=errors*1e3, y=obs_variances*1e3, linetype=alg)) +
  geom_line(size=0.6, alpha=0.9) +
  scale_linetype_manual(values=c("longdash", "solid", "dotdash"), name="Algorithm") +
  theme_classic() +
  labs(x="Error (ms)", y="Variance (ms)") -> p2

plot_grid <- rbind(
  c(1, 1, 1, NA, NA, NA, NA),
  c(1, 1, 1, 2, 2, 2, 2),
  c(1, 1, 1, 2, 2, 2, 2),
  c(1, 1, 1, 2, 2, 2, 2))

grid.arrange(p1, p2, layout_matrix=plot_grid)
rm(p1, p2, plot_grid)
```
